### 2019-08-14 reports/thesis/book.tex
conclusion

\chapter{Evaluation}
\label{chapter6}

>>>>

\chapter{Conclusion}
\label{chapter6}
To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment. A test sample was designed using a CAD model and was manufactured with purposefully designed voids. Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}. The obtained projections was used to help align the simulated projection. The aim of the experiment was to develop a statistical method to detect these designed voids.

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:evaluation_flowchart}
\end{figure}

Shading correction was required to remove spot and panel effects from the obtained projections. This was done by using the greyscale projections from a number of powers of the x-ray tube. By assuming each pixel has a linear response to the power, a linear regression was used. This is discussed in Chapter \ref{chapter2}.

In Chapter \ref{chapter3}, it was attempted to fit a compound Poisson distributed onto the grey values of a projection to quantify the noise. Unfortunately, the model suffered from identifiability issues for high photon counts. However, it was found that the grey value variance has a linear relationship with the grey value. In Chapter \ref{chapter4}, various GLM were fitted onto the variance-mean data and it was verified a linear relationship is a good model. The model was used as a tool to predict the variance of a grey value.

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection under the face of uncertainty. The uncertainty was predicted using the variance-mean model. Inference was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the inference to pick out areas which are unusual and unlike its neighbours. The filtered test statistics was converted to $p$-values so that hypothesis testing can be done to detect the voids.

In the ABS test sample, voids of the order of millimetres were detectable using this method. However, for the titanium test sample, the voids were undetectable due to dominating edge effects. The reason for this is unknown. It was speculated that the main source of error was from the simulated projection not being quite pixel-perfect aligned causing model misspecification at the edges. Therefore, the method was unable to distinguish disagreement due to model misspecification or a void. This method could be improved if \emph{aRTist} was integrated into it. For example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden in a particular angle.

The experiment could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true positives and false positives and the analysis can be quantified using a ROC curve.

This thesis is a contribution to real-time quality control for additive manufacturing. A powerful multi-core computer could be used to conduct the statistical analysis of x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.

### 2019-08-14 reports/thesis/chapters/5_inference.tex
printResults corrected in BandwidthSelection2
conclusion

\begin{table}
  \centering
  \input{../figures/inference/BandwidthSelection2_bandwidthEstimate.txt}
  \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
  \label{table:inference_BandwidthSelection2_ruleOfThumb}
\end{table}

@@

To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart of the process of the experiment and defect detection and how the empirical null filter fits in. The CAD model was used as a blueprint for the manufacture of the test sample. Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty. The uncertainty was modelled using the replicated projections. The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values. A threshold was used for the $p$-values to classify pixels as positive for defects or not.

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:inference_flowchart}
\end{figure}

@@

While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecification null statistics cannot be distinguished from non-null statistics.

>>>>

\begin{table}
  \centering
  \begin{tabular}{l|l}
           &Estimate \\ \hline
  Intercept&\input{../figures/inference/BandwidthSelection2_coeff1.txt}\\
  Gradient &\input{../figures/inference/BandwidthSelection2_coeff2.txt}
  \end{tabular}
  \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
  \label{table:inference_BandwidthSelection2_ruleOfThumb}
\end{table}

@@

@@

While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecified null statistics cannot be distinguished from non-null statistics. Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}.
